SU($n$) ferromagnets near the Heisenberg point

### 2020-07-22 collective_sun/sun_perturbation.tex
changes to figure names

The basic idea will be to identify the set of states (manifolds)
$\M_r$ with a definite number ($r$) of spin-wave excitations, or {\it
  magnons}.  The ground-state manifold of PS states is simply the
zero-magnon manifold $\M_0$.  If we construct a basis for all $\M_r$
with $r\le r_{\t{max}}$, we can perform numerical simulations in the
combined manifold of all states with at most $r_{\t{max}}$ magnons; we
refer to such simulations as {\it order-}$r_{\t{max}}$ {\it truncated
  shell} (TS$_{r_{\t{max}}}$) simulations.  An $M$-spin operator
$\O\p{\m w,X}$ can only couple $r$-magnon states (in $\M_r$) to
$q$-magnon states (in $\M_q$) with $\abs{q-r}\le M$.  For initially PS
states, TS$_{r_{\t{max}}}$ simulations thus capture all virtual
processes through order $2\floor{r_{\t{max}}/M}+1$ in perturbation
theory, when $\norm{\O\p{\m w,X}}<\Delta_{\t{gap}}/2$.  When
$\norm{\O\p{\m w,X}}\ge\Delta_{\t{gap}}/2$, perturbation theory
formally breaks down, and the error incurred by neglecting all
$s$-magnon states with $s>r_{\t{max}}$ is not clear a priori.
Nonetheless, TS$_{r_{\t{max}}}$ simulations can be benchmarked by
examining the populations of all $r$-magnon manifolds $\M_r$ with
$r\le r_{\t{max}}$.  As long as the maximal populations within
large-$r$ manifolds $\M_r$ are small, one should expect
TS$_{r_{\t{max}}}$ simulations to faithfully capture (at least
qualitatively) the dynamical behavior of the spin system under
consideration.

@@

Here we simplify the single-body product
\begin{align}
  \O\p{\m v,X} \O\p{\m w,Y}
  = \sum_{i,j} v_i w_j X_i Y_j
  \EQPS \diagram{single_body_0} X_1 Y_2
  + \diagram{single_body_1} X_1 Y_1,
\end{align}
where $i,j$ index individual spins that the single-spin operators
$X,Y$ act on; and $\m m\equiv\sum_i m_i\ket{i}$ for
$\m m\in\set{\m v,\m w}$ are vectors of scalar coefficients.  This
product appears, for example, in the calculation of the second-order
effective Hamiltonian $H_1^{(2)}$ induced on the permutationally
symmetric manifold $\M_0$ by a single-body perturbation.  Using the
rules that we worked out in Appendix \ref{sec:diagrams} for reducing
diagrams, we can simplify
\begin{align}
  \diagram{single_body_0}
  = \diagram{single_body_0_o} - \diagram{single_body_0_x}
  = \diagram{single_body_0_oo} - \diagram{single_body_1}
  = \col{v}\,\col{w} - \m v \c \m w,
\end{align}
where $\col{m} \equiv \sum_i m_i$ for both $\m m\in\set{\m v,\m w}$,
so
\begin{align}
  \O\p{\m v,X} \O\p{\m w,Y}
  \EQPS \p{\col{v}\,\col{w} - \m v\c\m w} X_1 Y_2
  + \m v\c\m w X_1 Y_1.
\end{align}
In order to write this result in terms of collective operators
$\col{Z} \equiv \sum_i Z_i$, we expand
\begin{align}
  \col{X Y} \EQPS N X_1 Y_1,
  &&
  \col{X}\,\col{Y} \EQPS \col{XY} + N\p{N-1} X_1 Y_2,
\end{align}
which implies that
\begin{align}
  \O\p{\m v,X} \O\p{\m w,Y}
  &\EQPS \f{\col{v}\,\col{w} - \m v\c\m w}{N\p{N-1}} \,
  \col{X}\, \col{Y}
  - \f{\col{v}\,\col{w} - N \m v\c\m w}{N\p{N-1}} \, \col{XY} \\
  &\EQPS \f{\col{v}\,\col{w}}{N\p{N-1}}
  \p{\col{X}\,\col{Y} - \col{XY}}
  - \f{\m v\c\m w}{N\p{N-1}}
  \p{\col{X}\,\col{Y} - N\col{XY}}.
\end{align}

@@

Here we simplify the two-body product
\begin{align}
  \O\p{\m v,X} \O\p{\m w,Y}
  = \sum_{i\ne j} \sum_{k\ne\ell}
  v_{ij} w_{k\ell} X_{ij} Y_{k\ell},
\end{align}
where $i,j,k,\ell$ index individual spins that the two-spin operators
$X,Y$ act on; and $\m m\equiv\sum_{i,j}m_{ij}\op{i}{j}$ for
$\m m\in\set{\m v,\m w}$ are matrices of scalar coefficients, with
$m_{ii}=0$.  This product appears, for example, in the calculation of
the second-order effective Hamiltonian $H_2^{(2)}$ induced on the
permutationally symmetric manifold $\M_0$ by a two-body perturbation.
The diagrammatic expansion of this operator is
\begin{align}
  \O\p{\m v,X} \O\p{\m w,Y}
  \EQPS \diagram{two_body_0} \spp{X,Y}_4 + \diagram{two_body_1}
  \spp{X,Y}_3 + \diagram{two_body_2} \spp{X,Y}_2,
  \label{eq:two_prod_pair}
\end{align}
where $\spp{X,Y}_q$ denotes a sum over all $q$-spin operators that can
be constructed from $X$ and $Y$, i.e.
\begin{align}
  \spp{X,Y}_4 \EQPS X_{1,2} Y_{3,4}, &&
  \spp{X,Y}_2 \EQPS X_{1,2} Y_{1,2} + X_{1,2} Y_{2,1},
\end{align}
\begin{align}
  \spp{X,Y}_3 \EQPS X_{1,2} Y_{1,3} + X_{1,2} Y_{3,1}
  + X_{1,2} Y_{2,3} + X_{1,2} Y_{3,2}.
\end{align}
To minimize the computational cost of the diagrams in
\eqref{eq:two_prod_pair}, we reduce
\begin{align}
  \diagram{two_body_1}
  &= \sp{\diagram{two_body_1_o}} - \sp{\diagram{two_body_1_x}} \\
  &= \sp{\diagram{two_body_1_oo} - \diagram{two_body_1_ox}}
  - \sp{\diagram{two_body_2}} \label{eq:mid_zero} \\
  &= \diagram{two_body_1_ooo} - \diagram{two_body_2_oo}
\end{align}
where the middle diagram in \eqref{eq:mid_zero} is zero from the fact
that $w_{ii}=0$, and
\begin{align}
  \diagram{two_body_0}
  &= \sp{\diagram{two_body_0_o}} - \sp{\diagram{two_body_0_x}} \\
  &= \sp{\diagram{two_body_0_oo} - \diagram{two_body_0_ox}}
  - \sp{2 \diagram{two_body_1}} \\
  &= \sp{\diagram{two_body_0_oooo} - 2 \diagram{two_body_1_o}}
  - \sp{2 \diagram{two_body_1_ooo} - 2 \diagram{two_body_2_oo}} \\
  &= \diagram{two_body_0_oooo} - 4 \diagram{two_body_1_ooo}
  + 2 \diagram{two_body_2_oo}.
\end{align}
If the matrices $\m v,\m w$ are symmetric, then we can define
\begin{align}
  \v{\m m} \equiv \sum_{i\ne j} m_{ij} \ket{ij},
  &&
  \v m \equiv \sum_{i,j} m_{ij} \ket{i},
  &&
  \col{m} \equiv \sum_{i,j} m_{ij},
\end{align}
for both $\m m\in\set{\m v,\m w}$, and expand
\begin{align}
  \diagram{two_body_2} = \v{\m v} \c\v{\m w},
  &&
  \diagram{two_body_1} =
  \v v \c \v w - \v{\m v} \c \v{\m w},
  &&
  \diagram{two_body_0}
  = \col{v}\,\col{w} - 4 \v v\c\v w + 2 \v{\m v}\c\v{\m w}.
\end{align}
In the special case that $X=Y=Z\otimes Z$ with a single-spin operator
$Z$ for which $Z^2=1$, we can simplify
\begin{align}
  \spp{Z\otimes Z,Z\otimes Z}_4 \EQPS Z^{\otimes 4},
  &&
  \spp{Z\otimes Z,Z\otimes Z}_3 \EQPS 4 Z^{\otimes 2},
  &&
  \spp{Z\otimes Z,Z\otimes Z}_2 \EQPS 2,
\end{align}
which implies that
\begin{align}
  \O\p{\m v,Z\otimes Z} \O\p{\m w,Z\otimes Z}
  \EQPS A_4 Z^{\otimes 4} + A_2 Z^{\otimes 2} + A_0,
\end{align}
with
\begin{align}
  A_4 \equiv \diagram{two_body_0}
  = \col{v}\,\col{w} - 4 \v v\c\v w + 2 \v{\m v}\c\v{\m w},
  &&
  A_2 \equiv 4 \diagram{two_body_1}
  = 4 \v v \c \v w - 4 \v{\m v} \c \v{\m w}
\end{align}
\begin{align}
  A_0 \equiv 2 \diagram{two_body_2} = 2 \v{\m v} \c\v{\m w}.
\end{align}
In terms of collective operators $\col{Z}\equiv\sum_iZ_i$, we have
\begin{align}
  \O\p{\m v,Z\otimes Z} \O\p{\m w,Z\otimes Z}
  \EQPS \tilde A_4 \col{Z}^4 + \tilde A_2 \col{Z}^2 + \tilde A_0,
\end{align}
where
\begin{align}
  \tilde A_4 \equiv \f{A_4}{N!_4},
  &&
  \tilde A_2 \equiv \f{A_2}{N!_2} - 2\p{3N-4} \f{A_4}{N!_4},
  &&
  \tilde A_0 \equiv A_0 - \f{A_2}{N-1} + \f{3A_4}{\p{N-1}\p{N-3}},
\end{align}
and
\begin{align}
  N!_q \equiv \sum_{j=0}^{q-1} \p{N-j}
\end{align}
is a falling factorial.

@@

Here we simplify the product
\begin{align}
  \O\p{\m u,\m v,\m w,Z}
  &\equiv \O\p{\m u,Z\otimes Z} \O\p{\m v,Z\otimes Z}
  \O\p{\m w,Z\otimes Z} \\
  &= \sum_{i\ne j} \sum_{k\ne\ell} \sum_{p\ne q}
  u_{ij} v_{k\ell} w_{pq} Z_i Z_j Z_k Z_\ell Z_p Z_q,
\end{align}
projected onto the PS manifold $\M_0$, where $i,j,k,\ell,p,q$ index
individual spins; $Z$ is a single-spin Ising-like operator, with
$Z^2=1$; and $\m m\equiv\sum_{i,j} m_{ij}\op{i}{j}$ for
$\m m\in\set{\m u,\m v,\m w}$ are matrices of scalar coefficients,
with $m_{ii}=0$.  This product appears, for example, in the projection
of Ising interactions onto the two-magnon manifold $\M_2$.  Collecting
terms according to the number of $Z$ operators that remain after
accounting for $Z^2=1$, we find that
\begin{align}
  \O\p{\m u,\m v,\m w,Z}
  \EQPS A_6 Z^{\otimes 6} + A_4 Z^{\otimes 4} + A_2 Z^{\otimes 2} + A_0,
  \label{eq:triple_multi}
\end{align}
with
\begin{align}
  A_6 \equiv \diagram{triple_0},
  &&
  A_4 \equiv 4 \diagram{triple_01} + 8 \diagram{triple_1},
  &&
  A_0 \equiv 8 \diagram{triple_0111},
  \label{eq:triple_64}
\end{align}
\begin{align}
  A_2 \equiv 8 \diagram{triple_011} + 2 \diagram{triple_02}
  + 8 \diagram{triple_11} + 4 \diagram{triple_2},
  \label{eq:triple_2}
\end{align}
where a diagram with unlabeled circles denotes a sum over all distinct
label assignments, e.g.
\begin{align}
  \diagram{triple_1} \equiv \diagram{triple_1_uvw},
  \label{eq:triple_uvw}
\end{align}
\begin{align}
  \diagram{triple_011}
  \equiv \diagram{triple_011_uvw}
  + \diagram{triple_011_vwu} + \diagram{triple_011_wuv}.
  \label{eq:triple_uvw_3}
\end{align}
The last diagram in each of $A_6,A_4,A_2,A_0$ as written in
\eqref{eq:triple_64}, \eqref{eq:triple_2} thus has only one assignment
of labels, as in \eqref{eq:triple_uvw}, while all other unlabeled
diagrams have three assignments, as in \eqref{eq:triple_uvw_3}.

Having identified diagrammatic representations of the coefficients
$A_6,A_4,A_2,A_0$, we now need to simplify all diagrams to reduce
their computational complexity, as discussed in Appendix
\ref{sec:diagrams}.  The process of eliminating filled dots and
crosses from a diagram is algorithmic enough to execute on a computer,
doing which we find
\begin{align}
  A_6 = D_6 - D_4 + D_2 - D_0,
  &&
  A_4 = D_4 - 2 D_2 + 3 D_0,
  &&
  A_2 = D_2 - 3 D_0,
  &&
  A_0 \equiv D_0,
\end{align}
where
\begin{align}
  D_6 \equiv \diagram{triple_0_o},
  &&
  D_4 \equiv 4 \diagram{triple_01_o} - 16 \diagram{triple_1_o},
  &&
  D_0 \equiv 8 \diagram{triple_0111_o},
\end{align}
\begin{align}
  D_2 \equiv 8 \diagram{triple_011_o}
  + 2 \diagram{triple_02_o}
  - 16 \diagram{triple_11_o}
  + 16 \diagram{triple_2_o}.
\end{align}
If $m_{ij}=m_{ji}$ for all $\m m\in\set{\m u,\m v,\m w}$, then we can
define
\begin{align}
  \v{\m m} \equiv \sum_{i\ne j} m_{ij} \ket{ij},
  &&
  \v m \equiv \sum_i m_i \ket{i},
  &&
  m_i \equiv \sum_j m_{ij},
  &&
  \col{m} \equiv \sum_{i,j} m_{ij},
\end{align}
and expand
\begin{align}
  D_6 = \col{u}\,\col{v}\,\col{w},
  &&
  D_4 = 4\p{\col{u}\,\v v\c\v w + \col{v}\,\v w\c\v u
  + \col{w}\,\v u\c\v v} - 16 \sum_i u_i v_i w_i,
  &&
  D_0 = 8 \tr\p{\m u \c \m v \c \m w},
\end{align}
\begin{multline}
  D_2 = 8\p{\v u \c\m v\c\v w + \v v \c\m w\c\v u + \v w \c\m u\c\v v}
  + 2\p{\col{u}\,\v{\m v}\c\v{\m w} + \col{v}\,\v{\m w}\c\v{\m u}
  + \col{w}\,\v{\m u}\c\v{\m v}} \\
  - 16 \sum_{i,j} \p{u_i v_{ij} w_{ij}
    + v_i w_{ij} u_{ij} + w_i u_{ij} v_{ij}}
  + 16 \sum_{i,j} u_{ij} v_{ij} w_{ij}.
\end{multline}
Finally, we can also write the product $\O\p{\m u,\m v,\m w,Z}$ in
terms of the collective operator $\col{Z} \equiv \sum_i Z_i$:
\begin{align}
  \O\p{\m u,\m v,\m w,Z}
  \EQPS \tilde A_6 \col{Z}^6 + \tilde A_4 \col{Z}^4
  + \tilde A_2 \col{Z}^2 + \tilde A_0,
\end{align}
where
\begin{align}
  \tilde A_6 \equiv \f{A_6}{N!_6},
  &&
  \tilde A_4 \equiv \f{A_4}{N!_4} - 5\p{3N-8} \f{A_6}{N!_6},
\end{align}
\begin{align}
  \tilde A_2 \equiv \f{A_2}{N!_2} - 2\p{3N-4} \f{A_4}{N!_4}
  + \p{45N^2-210N+184} \f{A_6}{N!_6},
\end{align}
\begin{align}
  \tilde A_0 \equiv A_0 - \f{A_2}{N-1}
  + \f{3A_4}{\p{N-1}\p{N-3}}
  - \f{15A_6}{\p{N-1}\p{N-3}\p{N-5}}.
\end{align}
and
\begin{align}
  N!_q \equiv \sum_{j=0}^{q-1} \p{N-j}
\end{align}
is a falling factorial.

>>>>

The basic idea will be to identify the set of states (manifolds)
$\M_r$ with a definite number ($r$) of spin-wave excitations, or {\it
  magnons}.  The ground-state manifold of PS states is simply the
zero-magnon manifold $\M_0$.  If we construct a basis for all $\M_r$
with $r\le r_{\t{max}}$, we can perform numerical simulations in the
combined manifold of all states with at most $r_{\t{max}}$ magnons; we
refer to such simulations as {\it order-}$r_{\t{max}}$ {\it truncated
  shell} (TS$_{r_{\t{max}}}$) simulations.  An $M$-spin operator
$\O\p{\m w,X}$ can only couple $r$-magnon states (in $\M_r$) to
$q$-magnon states (in $\M_q$) with $\abs{q-r}\le M$.  For initially PS
states, TS$_{r_{\t{max}}}$ simulations thus capture all virtual
processes through order $2\floor{r_{\t{max}}/M}+1$ in perturbation
theory.  When $\norm{\O\p{\m w,X}}\ge\Delta_{\t{gap}}/2$, however,
perturbation theory formally breaks down, and the error incurred by
neglecting all $s$-magnon states with $s>r_{\t{max}}$ is not clear a
priori.  Nonetheless, TS$_{r_{\t{max}}}$ simulations can be
benchmarked by examining the populations of all $r$-magnon manifolds
$\M_r$ with $r\le r_{\t{max}}$.  As long as the maximal populations
within large-$r$ manifolds $\M_r$ are small, one should expect
TS$_{r_{\t{max}}}$ simulations to faithfully capture (at least
qualitatively) the dynamical behavior of the spin system under
consideration.

@@

Here we simplify the single-body product
\begin{align}
  \O\p{\m v,X} \O\p{\m w,Y}
  = \sum_{i,j} v_i w_j X_i Y_j
  \EQPS \diagram{prod_b11_c0} X_1 Y_2
  + \diagram{prod_b11_c1} X_1 Y_1,
\end{align}
where $i,j$ index individual spins that the single-spin operators
$X,Y$ act on; and $\m m\equiv\sum_i m_i\ket{i}$ for
$\m m\in\set{\m v,\m w}$ are vectors of scalar coefficients.  This
product appears, for example, in the calculation of the second-order
effective Hamiltonian $H_1^{(2)}$ induced on the permutationally
symmetric manifold $\M_0$ by a single-body perturbation.  Using the
rules that we worked out in Appendix \ref{sec:diagrams} for reducing
diagrams, we can simplify
\begin{align}
  \diagram{prod_b11_c0}
  = \diagram{prod_b11_c0_o} - \diagram{prod_b11_c0_x}
  = \diagram{prod_b11_c0_oo} - \diagram{prod_b11_c1}
  = \col{v}\,\col{w} - \m v \c \m w,
\end{align}
where $\col{m} \equiv \sum_i m_i$ for both $\m m\in\set{\m v,\m w}$,
so
\begin{align}
  \O\p{\m v,X} \O\p{\m w,Y}
  \EQPS \p{\col{v}\,\col{w} - \m v\c\m w} X_1 Y_2
  + \m v\c\m w X_1 Y_1.
\end{align}
In order to write this result in terms of collective operators
$\col{Z} \equiv \sum_i Z_i$, we expand
\begin{align}
  \col{X Y} \EQPS N X_1 Y_1,
  &&
  \col{X}\,\col{Y} \EQPS \col{XY} + N\p{N-1} X_1 Y_2,
\end{align}
which implies that
\begin{align}
  \O\p{\m v,X} \O\p{\m w,Y}
  &\EQPS \f{\col{v}\,\col{w} - \m v\c\m w}{N\p{N-1}} \,
  \col{X}\, \col{Y}
  - \f{\col{v}\,\col{w} - N \m v\c\m w}{N\p{N-1}} \, \col{XY} \\
  &\EQPS \f{\col{v}\,\col{w}}{N\p{N-1}}
  \p{\col{X}\,\col{Y} - \col{XY}}
  - \f{\m v\c\m w}{N\p{N-1}}
  \p{\col{X}\,\col{Y} - N\col{XY}}.
\end{align}

@@

Here we simplify the two-body product
\begin{align}
  \O\p{\m v,X} \O\p{\m w,Y}
  = \sum_{i\ne j} \sum_{k\ne\ell}
  v_{ij} w_{k\ell} X_{ij} Y_{k\ell},
\end{align}
where $i,j,k,\ell$ index individual spins that the two-spin operators
$X,Y$ act on; and $\m m\equiv\sum_{i,j}m_{ij}\op{i}{j}$ for
$\m m\in\set{\m v,\m w}$ are matrices of scalar coefficients, with
$m_{ii}=0$.  This product appears, for example, in the calculation of
the second-order effective Hamiltonian $H_2^{(2)}$ induced on the
permutationally symmetric manifold $\M_0$ by a two-body perturbation.
The diagrammatic expansion of this operator is
\begin{align}
  \O\p{\m v,X} \O\p{\m w,Y}
  \EQPS \diagram{prod_b22_c0} \spp{X,Y}_4 + \diagram{prod_b22_c1}
  \spp{X,Y}_3 + \diagram{prod_b22_c2} \spp{X,Y}_2,
  \label{eq:two_prod_pair}
\end{align}
where $\spp{X,Y}_q$ denotes a sum over all $q$-spin operators that can
be constructed from $X$ and $Y$, i.e.
\begin{align}
  \spp{X,Y}_4 \EQPS X_{1,2} Y_{3,4}, &&
  \spp{X,Y}_2 \EQPS X_{1,2} Y_{1,2} + X_{1,2} Y_{2,1},
\end{align}
\begin{align}
  \spp{X,Y}_3 \EQPS X_{1,2} Y_{1,3} + X_{1,2} Y_{3,1}
  + X_{1,2} Y_{2,3} + X_{1,2} Y_{3,2}.
\end{align}
To minimize the computational cost of the diagrams in
\eqref{eq:two_prod_pair}, we reduce
\begin{align}
  \diagram{prod_b22_c1}
  &= \sp{\diagram{prod_b22_c1_o}} - \sp{\diagram{prod_b22_c1_x}} \\
  &= \sp{\diagram{prod_b22_c1_oo} - \diagram{prod_b22_c1_ox}}
  - \sp{\diagram{prod_b22_c2}} \label{eq:mid_zero} \\
  &= \diagram{prod_b22_c1_ooo} - \diagram{prod_b22_c2_oo}
\end{align}
where the middle diagram in \eqref{eq:mid_zero} is zero from the fact
that $w_{ii}=0$, and
\begin{align}
  \diagram{prod_b22_c0}
  &= \sp{\diagram{prod_b22_c0_o}} - \sp{\diagram{prod_b22_c0_x}} \\
  &= \sp{\diagram{prod_b22_c0_oo} - \diagram{prod_b22_c0_ox}}
  - \sp{2 \diagram{prod_b22_c1}} \\
  &= \sp{\diagram{prod_b22_c0_oooo} - 2 \diagram{prod_b22_c1_o}}
  - \sp{2 \diagram{prod_b22_c1_ooo} - 2 \diagram{prod_b22_c2_oo}} \\
  &= \diagram{prod_b22_c0_oooo} - 4 \diagram{prod_b22_c1_ooo}
  + 2 \diagram{prod_b22_c2_oo}.
\end{align}
If the matrices $\m v,\m w$ are symmetric, then we can define
\begin{align}
  \v{\m m} \equiv \sum_{i\ne j} m_{ij} \ket{ij},
  &&
  \v m \equiv \sum_{i,j} m_{ij} \ket{i},
  &&
  \col{m} \equiv \sum_{i,j} m_{ij},
\end{align}
for both $\m m\in\set{\m v,\m w}$, and expand
\begin{align}
  \diagram{prod_b22_c2} = \v{\m v} \c\v{\m w},
  &&
  \diagram{prod_b22_c1} =
  \v v \c \v w - \v{\m v} \c \v{\m w},
  &&
  \diagram{prod_b22_c0}
  = \col{v}\,\col{w} - 4 \v v\c\v w + 2 \v{\m v}\c\v{\m w}.
\end{align}
In the special case that $X=Y=Z\otimes Z$ with a single-spin operator
$Z$ for which $Z^2=1$, we can simplify
\begin{align}
  \spp{Z\otimes Z,Z\otimes Z}_4 \EQPS Z^{\otimes 4},
  &&
  \spp{Z\otimes Z,Z\otimes Z}_3 \EQPS 4 Z^{\otimes 2},
  &&
  \spp{Z\otimes Z,Z\otimes Z}_2 \EQPS 2,
\end{align}
which implies that
\begin{align}
  \O\p{\m v,Z\otimes Z} \O\p{\m w,Z\otimes Z}
  \EQPS A_4 Z^{\otimes 4} + A_2 Z^{\otimes 2} + A_0,
\end{align}
with
\begin{align}
  A_4 \equiv \diagram{prod_b22_c0}
  = \col{v}\,\col{w} - 4 \v v\c\v w + 2 \v{\m v}\c\v{\m w},
  &&
  A_2 \equiv 4 \diagram{prod_b22_c1}
  = 4 \v v \c \v w - 4 \v{\m v} \c \v{\m w}
\end{align}
\begin{align}
  A_0 \equiv 2 \diagram{prod_b22_c2} = 2 \v{\m v} \c\v{\m w}.
\end{align}
In terms of collective operators $\col{Z}\equiv\sum_iZ_i$, we have
\begin{align}
  \O\p{\m v,Z\otimes Z} \O\p{\m w,Z\otimes Z}
  \EQPS \tilde A_4 \col{Z}^4 + \tilde A_2 \col{Z}^2 + \tilde A_0,
\end{align}
where
\begin{align}
  \tilde A_4 \equiv \f{A_4}{N!_4},
  &&
  \tilde A_2 \equiv \f{A_2}{N!_2} - 2\p{3N-4} \f{A_4}{N!_4},
  &&
  \tilde A_0 \equiv A_0 - \f{A_2}{N-1} + \f{3A_4}{\p{N-1}\p{N-3}},
\end{align}
and
\begin{align}
  N!_q \equiv \sum_{j=0}^{q-1} \p{N-j}
\end{align}
is a falling factorial.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsection{Three single-body operators}
% \label{sec:single_trip_prod}

% Here we simplify the single-body product
% \begin{align}
%   \O\p{\m u,X} \O\p{\m v,Y} \O\p{\m w,Z}
%   = \sum_{i,j,k} u_i v_j w_k X_i Y_j Z_k,
% \end{align}
% where $i,j,k$ index individual spins that the single-spin operators
% $X,Y,K$ act on; and $\m m\equiv\sum_i m_i\ket{i}$ for
% $\m m\in\set{\m u,\m v,\m w}$ are vectors of scalar coefficients.
% This product appears, for example, in the calculation of matrix
% elements of the operator $\O\p{\m v,Y}$ within the single-magnon
% manifold.  The diagrammatic expansion of this operator is
% \begin{multline}
%   \O\p{\m u,X} \O\p{\m v,Y} \O\p{\m w,Z}
%   \EQPS \diagram{prod_b111_c0} X_1 Y_2 Z_3
%   + \diagram{prod_b111_c10} X_1 Y_1 Z_1 \\
%   + \diagram{prod_b111_c11_u} X_1 Y_2 Z_2
%   + \diagram{prod_b111_c11_v} X_2 Y_1 Z_2
%   + \diagram{prod_b111_c11_w} X_2 Y_2 Z_1,
% \end{multline}
% where we can reduce (by hand or with a computer)

@@

Here we simplify the product
\begin{align}
  \O\p{\m u,\m v,\m w,Z}
  &\equiv \O\p{\m u,Z\otimes Z} \O\p{\m v,Z\otimes Z}
  \O\p{\m w,Z\otimes Z} \\
  &= \sum_{i\ne j} \sum_{k\ne\ell} \sum_{p\ne q}
  u_{ij} v_{k\ell} w_{pq} Z_i Z_j Z_k Z_\ell Z_p Z_q,
\end{align}
projected onto the PS manifold $\M_0$, where $i,j,k,\ell,p,q$ index
individual spins; $Z$ is a single-spin Ising-like operator, with
$Z^2=1$; and $\m m\equiv\sum_{i,j} m_{ij}\op{i}{j}$ for
$\m m\in\set{\m u,\m v,\m w}$ are matrices of scalar coefficients,
with $m_{ii}=0$.  This product appears, for example, in the projection
of Ising interactions onto the two-magnon manifold $\M_2$.  Collecting
terms according to the number of $Z$ operators that remain after
accounting for $Z^2=1$, we find that
\begin{align}
  \O\p{\m u,\m v,\m w,Z}
  \EQPS A_6 Z^{\otimes 6} + A_4 Z^{\otimes 4} + A_2 Z^{\otimes 2} + A_0,
  \label{eq:triple_multi}
\end{align}
with
\begin{align}
  A_6 \equiv \diagram{prod_b222_c0},
  &&
  A_4 \equiv 4 \diagram{prod_b222_c01} + 8 \diagram{prod_b222_c1},
  &&
  A_0 \equiv 8 \diagram{prod_b222_c0111},
  \label{eq:triple_64}
\end{align}
\begin{align}
  A_2 \equiv 8 \diagram{prod_b222_c011} + 2 \diagram{prod_b222_c02}
  + 8 \diagram{prod_b222_c11} + 4 \diagram{prod_b222_c2},
  \label{eq:triple_2}
\end{align}
where a diagram with unlabeled circles denotes a sum over all distinct
label assignments, e.g.
\begin{align}
  \diagram{prod_b222_c1} \equiv \diagram{prod_b222_c1_uvw},
  \label{eq:triple_uvw}
\end{align}
\begin{align}
  \diagram{prod_b222_c011}
  \equiv \diagram{prod_b222_c011_uvw}
  + \diagram{prod_b222_c011_vwu} + \diagram{prod_b222_c011_wuv}.
  \label{eq:triple_uvw_3}
\end{align}
The last diagram in each of $A_6,A_4,A_2,A_0$ as written in
\eqref{eq:triple_64}, \eqref{eq:triple_2} thus has only one assignment
of labels, as in \eqref{eq:triple_uvw}, while all other unlabeled
diagrams have three assignments, as in \eqref{eq:triple_uvw_3}.

Having identified diagrammatic representations of the coefficients
$A_6,A_4,A_2,A_0$, we now need to simplify all diagrams to reduce
their computational complexity, as discussed in Appendix
\ref{sec:diagrams}.  The process of eliminating filled dots and
crosses from a diagram is algorithmic enough to execute on a computer,
doing which we find
\begin{align}
  A_6 = D_6 - D_4 + D_2 - D_0,
  &&
  A_4 = D_4 - 2 D_2 + 3 D_0,
  &&
  A_2 = D_2 - 3 D_0,
  &&
  A_0 \equiv D_0,
\end{align}
where
\begin{align}
  D_6 \equiv \diagram{prod_b222_c0_o},
  &&
  D_4 \equiv 4 \diagram{prod_b222_c01_o} - 16 \diagram{prod_b222_c1_o},
  &&
  D_0 \equiv 8 \diagram{prod_b222_c0111_o},
\end{align}
\begin{align}
  D_2 \equiv 8 \diagram{prod_b222_c011_o}
  + 2 \diagram{prod_b222_c02_o}
  - 16 \diagram{prod_b222_c11_o}
  + 16 \diagram{prod_b222_c2_o}.
\end{align}
If $m_{ij}=m_{ji}$ for all $\m m\in\set{\m u,\m v,\m w}$, then we can
define
\begin{align}
  \v{\m m} \equiv \sum_{i\ne j} m_{ij} \ket{ij},
  &&
  \v m \equiv \sum_i m_i \ket{i},
  &&
  m_i \equiv \sum_j m_{ij},
  &&
  \col{m} \equiv \sum_{i,j} m_{ij},
\end{align}
and expand
\begin{align}
  D_6 = \col{u}\,\col{v}\,\col{w},
  &&
  D_4 = 4\p{\col{u}\,\v v\c\v w + \col{v}\,\v w\c\v u
  + \col{w}\,\v u\c\v v} - 16 \sum_i u_i v_i w_i,
  &&
  D_0 = 8 \tr\p{\m u \c \m v \c \m w},
\end{align}
\begin{multline}
  D_2 = 8\p{\v u \c\m v\c\v w + \v v \c\m w\c\v u + \v w \c\m u\c\v v}
  + 2\p{\col{u}\,\v{\m v}\c\v{\m w} + \col{v}\,\v{\m w}\c\v{\m u}
  + \col{w}\,\v{\m u}\c\v{\m v}} \\
  - 16 \sum_{i,j} \p{u_i v_{ij} w_{ij}
    + v_i w_{ij} u_{ij} + w_i u_{ij} v_{ij}}
  + 16 \sum_{i,j} u_{ij} v_{ij} w_{ij}.
\end{multline}
Finally, we can also write the product $\O\p{\m u,\m v,\m w,Z}$ in
terms of the collective operator $\col{Z} \equiv \sum_i Z_i$:
\begin{align}
  \O\p{\m u,\m v,\m w,Z}
  \EQPS \tilde A_6 \col{Z}^6 + \tilde A_4 \col{Z}^4
  + \tilde A_2 \col{Z}^2 + \tilde A_0,
\end{align}
where
\begin{align}
  \tilde A_6 \equiv \f{A_6}{N!_6},
  &&
  \tilde A_4 \equiv \f{A_4}{N!_4} - 5\p{3N-8} \f{A_6}{N!_6},
\end{align}
\begin{align}
  \tilde A_2 \equiv \f{A_2}{N!_2} - 2\p{3N-4} \f{A_4}{N!_4}
  + \p{45N^2-210N+184} \f{A_6}{N!_6},
\end{align}
\begin{align}
  \tilde A_0 \equiv A_0 - \f{A_2}{N-1}
  + \f{3A_4}{\p{N-1}\p{N-3}}
  - \f{15A_6}{\p{N-1}\p{N-3}\p{N-5}}.
\end{align}
and
\begin{align}
  N!_q \equiv \sum_{j=0}^{q-1} \p{N-j}
\end{align}
is a falling factorial.
